Truthfulness Verification System

### 2011-02-23 proposal/paper.tex
added conclusion and example in learing section

\subsection{Freebase} 
Freebase has information about approximately 20 million Topics, each one having a
unique Id, which can help distinguish multiple entities which have similar names,
such as Henry Ford the industrialist vs Henry Ford the footballer. Most of the
topics are associated with one or more types\cite{freebasetype} (such as
people, places, books, films, etc) and may have additional properties like "date of birth" for a person
or latitude and longitude for a location. Freebase not only contains data from
the Wikipedia but also other sources; users can submit data to the Freebase
datastore and expand it in richness. We tinkered with the api\cite{freebaseapi}
and it appeared to be the most viable starting point for the project.

\subsubsection{Motivational Example}

@@

     ...
    'E-m$0040il_f$00FCr_Dich',
    'youve-got-mail']
[   '176489',
    'Joe_Versus_the_Volcano',
    'Joe_Vs$002E_The_Volcano',
    'Brain_Cloud',
     ...
    '2327353',
    'joe-versus-the-volcano']
[   '226198',
    'Sleepless_in_Seattle',
    'Sleepless_In_Seattle',
     ....
    '169146',
    '106482',
    'Insonnia_d$0027amore',
    '62812',
    'Schlaflos_in_Seattle',
    'sleepless-in-seattle']

@@

\subsection{Dbpedia}
DBpedia is a similar project to Freebase, but it focuses mainly on the content
available from Wikipedia. It scores in being precisely importing the data from
the info boxes in Wikipedia pages, but at this stage it does not seem to be
offering anything additional over Freebase \cite{freebasedbpedia}. We are yet to
explore its programmatic interface \cite{dbpediaapi}.

\subsection{Yago}
YAGO is a semantic knowledge base with over 900,000 entities (like persons,
organizations, cities, etc.) and uses Wikipedia and Wordnet as its main source of
information. We are yet to explore the programmatic interfaces it provides and
how we can use it for the project.

\section{Truthfulness verification }
\subsection {Building queries from the data supplied by the user}

@@

\subsection{Application of Machine learning algorithms}
Though usage of machine learning algorithm seems to be very exciting approach at
this point, we are also skeptical about it. Supervised classifiers might not be
benficial for us due to the limited dataset for training and the potentialy
unlimited variety of inputs to classify. However, if we can use Graph
Based Partially Supervised Learning\cite{conf/acl/CelikyilmazTH09} or
Spreading Activation \cite{Cohen1987255} on the information extacted from the
rich ontologies is something we plan to explore.

>>>>

\subsubsection{Freebase} 
Freebase has information about approximately 20 million Topics, each one having a
unique Id, which can help distinguish multiple entities which have similar names,
such as Henry Ford the industrialist vs Henry Ford the footballer. Most of the
topics are associated with one or more types\cite{freebasetype} (such as
people, places, books, films, etc) and may have additional properties like "date of birth" for a person
or latitude and longitude for a location. Freebase not only contains data from
the Wikipedia but also other sources; users can submit data to the Freebase
datastore and expand it in richness. We tinkered with the api\cite{freebaseapi}
and it appeared to be the most viable starting point for the project.

\subparagraph{Motivational Example}

@@

     ...
    'E-m$0040il_f$00FCr_Dich',
    'youve-got-mail']
[   '176489',
    'Joe_Versus_the_Volcano',
    'Joe_Vs$002E_The_Volcano',
    'Brain_Cloud',
     ...
    '2327353',
    'joe-versus-the-volcano']
[   '226198',
    'Sleepless_in_Seattle',
    'Sleepless_In_Seattle',
     ....
    '169146',
    '106482',
    'Insonnia_d$0027amore',
    '62812',
    'Schlaflos_in_Seattle',
    'sleepless-in-seattle'\]

@@

\subsubsection{Dbpedia}
DBpedia is a similar project to Freebase, but it focuses mainly on the content
available from Wikipedia. It scores in being precisely importing the data from
the info boxes in Wikipedia pages, but at this stage it does not seem to be
offering anything additional over Freebase \cite{freebasedbpedia}. We are yet to
explore its programmatic interface \cite{dbpediaapi}.

\subsubsection{Yago}
YAGO is a semantic knowledge base with over 900,000 entities (like persons,
organizations, cities, etc.) and uses Wikipedia and Wordnet as its main source of
information. We are yet to explore the programmatic interfaces it provides and
how we can use it for the project.

\subsection{Truthfulness verification }
\subsubsection {Building queries from the data supplied by the user}

@@

\subsubsection{Application of Machine learning algorithms}
Though usage of machine learning algorithm seems to be a good approach at
this point. Consider the following example.

\emph{"Tom Hanks was the lead actress in the movie sleepless in Seattle"}

Now If the algorithm can learn that Tom hanks is a male and so he can't be an actress then our system should be able to classify the above statement as false.

However, we will need to explore more to be sure that we can apply machine learning algorithms successfully. Supervised classifiers might not be beneficial for us due to the limited dataset for training and the potentially unlimited variety of inputs to classify. However, if we can use Graph Based Partially Supervised Learning\cite{conf/acl/CelikyilmazTH09} or Spreading Activation \cite{Cohen1987255} on the information extracted from the rich ontologies is something we plan to explore.

\section{Conclusion}
It this paper, we described current system for truthfulness verification of statements found in the web called T-Verifier and described the possible improvements to the current system. We will primarily use authentic information sources such as Wikipedia and Ontologies extracted from Wikipedia such as FreeBase, DBPedia, and YOGA to found the truthfulness of doubtful statements.
